Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-09-25 paper/synthetic.tex
figures synthetic

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/AUC_R.png}
  \vspace{-4ex}
  \caption{Synthetic experiments. Distribution of differences in AUC (left) and Feature Importance (right) metrics between our method and the baselines. Mass under the dashed line corresponds to B2B outperforming the baseline. \label{fig:auc_plots}}
  \vspace{2ex}
  \includegraphics[width=\linewidth]{figures/AUC_conditions.png}
  \includegraphics[width=\linewidth]{figures/R_conditions.png}
  \vspace{-4ex}
  \caption{Synthetic experiments. Average AUC (top) and Feature Importance R (bottom) metrics as a function of experimental conditions. Higher is better. \label{fig:percondition}}
\end{figure}

@@

To address this issue, we assess the ability of each model to reliably predict
independent and identically distributed data from $Y$, given all of the $X$
features versus all but one feature: $X_k$ (i.e. 'knock-out X'). This procedure
results in two correlation metrics $R_{full}$ and $R_{knockout}$, whose
difference $\Delta R=R_{full}-R_{knockout}$ indicates how much $X_i$ improves
the prediction of $Y$ above and beyond what can be predicted from all other
features $X_k$.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/AUC_R.png}
  \vspace{-4ex}
  \caption{Synthetic experiments. Distribution of differences in AUC (left) and Feature Importance $\Delta R$ (right) metrics between our method and the baselines. Mass under the dashed line corresponds to B2B outperforming the baseline. \label{fig:auc_plots}}
  \vspace{2ex}
  \includegraphics[width=\linewidth]{figures/AUC_conditions}
  \includegraphics[width=\linewidth]{figures/R_conditions}
  \vspace{-4ex}
  \caption{Synthetic experiments. Average AUC (top) and Feature Importance $\Delta R$ (bottom) metrics as a function of experimental conditions. Higher is better. \label{fig:percondition}}
\end{figure}

@@

To address this issue, we assess the ability of each model to reliably predict
independent and identically distributed data from $Y$, given all of the $X$
features versus all-but-one feature: $X_k$ (i.e. 'knock-out X'). This procedure
results in two correlation metrics $R_{full}$ and $R_{knockout}$, whose
difference $\Delta R=R_{full}-R_{knockout}$ indicates how much $X_i$ improves
the prediction of $Y$% above and
beyond what can be predicted from all other
features $X_k$.
